\documentclass{article}
\usepackage{amsmath,amssymb,booktabs,graphicx}
\begin{document}

% ==============================================================================
\section{Coarse-Grained Lipid Model for Hybrid All-Atom / Dry MARTINI Simulations}
% ==============================================================================

\subsection{Single-Particle CG Lipid Representation}

Each DOPC lipid, comprising 14 MARTINI beads in the dry MARTINI force field~\cite{MARTINI},
is coarse-grained to a single oriented particle carrying a 6D state vector
$(\mathbf{r}, \hat{\mathbf{n}})$, where $\mathbf{r} \in \mathbb{R}^3$ is the
geometric center of the 14-bead lipid and $\hat{\mathbf{n}} \in S^2$ is a unit
direction vector from the NC3 head bead toward the midpoint of the terminal tail
beads C5A and C5B. The orientation vector is anchored by a hidden orientation
site (``CGLD'') placed at $\mathbf{r} + \ell\,\hat{\mathbf{n}}$ and connected
to the CG particle by a harmonic bond
\begin{equation}
  U_{\text{bond}} = \frac{1}{2} k_b (r - \ell)^2 .
\end{equation}

The CGLD parameters are derived from the same DOPC reference coordinates and
dry-MARTINI ITP data used to build the interaction tables.  Let
$\mathbf{x}_i$ be bead positions relative to the geometric center, $m_i$ the
dry-MARTINI bead masses, and $\hat{\mathbf{n}}$ the NC3-to-tail-midpoint unit
axis.  The orientation length, CGLD mass, and CGL-CGLD spring constant are
\begin{align}
  \ell &= \left| \mathbf{x}_{\text{tail}} \cdot \hat{\mathbf{n}} \right|, \\
  I_\perp &= \sum_i m_i \left(|\mathbf{x}_i|^2 -
             (\mathbf{x}_i \cdot \hat{\mathbf{n}})^2 \right), \\
  M_{\text{CGLD}} &= I_\perp / \ell^2, \\
  k_b &= \frac{1}{\kappa_E \kappa_L^2}
        \sum_{(i,j)\in\text{DOPC bonds}} k_{ij}
        \left( \hat{\mathbf{d}}_{ij}\cdot\hat{\mathbf{n}} \right)^2 ,
\end{align}
where $\mathbf{x}_{\text{tail}}$ is the midpoint of C5A and C5B relative to the
geometric center, $\hat{\mathbf{d}}_{ij}$ is the unit vector along DOPC bond
$(i,j)$, $k_{ij}$ is the dry-MARTINI bond force constant in
$\text{kJ/mol}/\text{nm}^2$, $\kappa_E = 2.914952774272\,\text{kJ/mol}/E_{\text{up}}$,
and $\kappa_L = 10\,\text{\AA}/\text{nm}$.

For \texttt{parameters/dryMARTINI/DOPC.pdb} and
\texttt{dry\_martini\_v2.1.itp}, this gives
$\ell = 11.139\,\text{\AA}$, $M_{\text{CGLD}} = 77.049\,\text{g/mol}$, and
$k_b = 39.436\,E_{\text{up}}/\text{\AA}^2$ for the canonical reference lipid.
These values are used for every single-particle DOPC preparation.  Packed
lipid conformations provide only the initial CGL positions and leaflet
directions; they do not redefine $\ell$, $M_{\text{CGLD}}$, $k_b$, display
span, or the interaction-table geometry.  This keeps the runtime CGLD
orientation carrier consistent with the canonical resolved DOPC model used to
fit the spline tables and makes the coarse lipid model independent of the
particular packed lipid distribution.  The CGL particle mass remains the sum of
the 14 DOPC bead masses; CGLD is an internal orientation-coordinate carrier
with zero nonbonded interactions, not an additional dry-MARTINI bead.

VTF trajectory output expands each CGL particle only for visualization.  The
displayed endpoints use a symmetric rod with the CGL center at the midpoint;
these display atoms are not simulation particles.  At periodic box boundaries a
continuous lipid display rod can legitimately have an endpoint outside the
primary image.  This is a periodic visualization artifact, not an extra force or
a physical box edge.

\paragraph{Derived Contact Distance.}
The single-particle lipid contact distance is derived from the dry-MARTINI DOPC
nonbonded parameters rather than set independently:
\begin{equation}
  r_{\text{contact}} = 2^{1/6} \max_{i,j\in\text{DOPC}} \sigma_{ij}.
\end{equation}
For the current dry-MARTINI DOPC bead types, $\max\sigma_{ij}=0.62\,\text{nm}$,
so $r_{\text{contact}}=6.959\,\text{\AA}$.  This value is used as the lower
support for CGL-CGL fitting and as the default same-leaflet initial spacing
conditioner.

\subsection{Angle Convention}

All orientation-dependent potentials use the same angle convention.  For a pair
of interacting oriented particles with positions $\mathbf{r}_1, \mathbf{r}_2$
and unit direction vectors $\hat{\mathbf{n}}_1, \hat{\mathbf{n}}_2$, define
the inter-particle unit vector $\hat{\mathbf{r}}_{12} = (\mathbf{r}_2 -
\mathbf{r}_1)/|\mathbf{r}_2 - \mathbf{r}_1|$.  The two angular coordinates are:
\begin{align}
  \cos\theta_1 &= -\hat{\mathbf{n}}_1 \cdot \hat{\mathbf{r}}_{12} \label{eq:ang1}\\
  \cos\theta_2 &= +\hat{\mathbf{n}}_2 \cdot \hat{\mathbf{r}}_{12} \label{eq:ang2}
\end{align}
Physically, when two lipids face each other head-to-head across the bilayer
midplane, $\cos\theta_1 \approx +1$ and $\cos\theta_2 \approx +1$.

\subsection{CG Lipid -- CG Lipid Tensor-Spline Potential}
\label{sec:cg-cg}

The interaction between two CG lipid particles is described by a full tensor
product cubic B-spline over distance and both lipid-facing angular coordinates:

\begin{equation}
\boxed{
U_{\text{CG-CG}}(r, \cos\theta_1, \cos\theta_2)
= \sum_{i=0}^{N_r-1}\sum_{j=0}^{N_\theta-1}\sum_{k=0}^{N_\theta-1}
  c_{ijk}\,B_i(r)\,B_j(\cos\theta_1)\,B_k(\cos\theta_2)
}
\label{eq:cg-cg}
\end{equation}

where $B_i$, $B_j$, and $B_k$ are cubic B-spline basis functions with clamped
de Boor boundary conditions~\cite{deBoor}.  The current table uses
$N_r = 14$ radial control points on $r \in [0, 16.8]\,\text{\AA}$ with
$\Delta r = 1.4\,\text{\AA}$, and $N_\theta = 15$ angular control points on
$\cos\theta \in [-1, 1]$.  The total stored coefficient count per CGL-CGL type
pair is $N_r N_\theta^2 = 3150$.

\paragraph{Tapering.}
A cubic Hermite taper $S(u) = u^2(3 - 2u)$ with
$u = (r_{\text{cut}} - r) / w$ smoothly drives the potential to zero at the cutoff;
the taper width $w = \Delta r = 1.4\,\text{\AA}$.

\paragraph{Table Construction.}
The potential is constructed from the underlying dry MARTINI force field by
sampling the total nonbonded energy (Lennard-Jones plus Coulomb) between two
explicit 14-bead DOPC lipids at a regular grid of $(r, \cos\theta_1,
\cos\theta_2)$ values.  Bead--bead terms are included only within the same
$12\,\text{\AA}$ dry-MARTINI nonbonded cutoff used by the runtime generic
MARTINI potential. The CGL--CGL grid is always sampled at the full
resolution ($16$ radial values, $7$ angular values, and $2$ azimuths per
lipid), including when reduced-resolution table generation is requested for
other terms, because reduced CGL--CGL angular sampling admits unphysical
same-leaflet overlaps. For each sampled configuration, the internal bead
coordinates are relaxed by steepest-descent energy minimization
($N_{\text{relax}} = 50$ steps). The sampled energy includes the dry-MARTINI
bonded deformation penalty relative to the unrelaxed DOPC reference, so local
steric stress can relax but deformation is not free.
Direction-vector azimuths are integrated as a dry-MARTINI energy
expectation:
\begin{equation}
U_{\text{CG-CG}}(r,\cos\theta_1,\cos\theta_2)
=
\left\langle
U_{\text{DOPC-DOPC}}(r,\cos\theta_1,\cos\theta_2,
\phi_1,\phi_2)
\right\rangle_{\phi_1,\phi_2}.
\end{equation}
Here $\phi_1$ and $\phi_2$ are the azimuths of the two CGL orientation vectors
around the interparticle axis.  The runtime potential takes the two CGL
direction vectors as input and evaluates their projections onto
$\hat{\mathbf{r}}_{12}$.  Table generation therefore rotates the resolved DOPC
bead model over these sampled direction vectors rather than deriving a table
from one default orientation.  Optional bead-frame quadrature around each
sampled direction vector can be enabled for convergence tests, but it is not a
separate runtime coordinate.
This avoids pairwise PMF overcounting of missing azimuthal relaxation in a
many-lipid additive Hamiltonian while still deriving the table directly from
the dry-MARTINI force field.  The attractive radial angular mean of each
sampled row is subtracted before fitting.  Positive radial means are left
unchanged.  This removes the isotropic cohesive background of an isolated
DOPC--DOPC pair, which is not transferable as an additive many-neighbor
single-particle membrane interaction, while preserving dry-MARTINI excluded
volume and orientation-dependent residuals.  After spline fitting, remaining
negative CGL--CGL controls are set to zero for the same reason: the CGL--CGL
node represents excluded-volume and orientation-compatibility physics in the
one-particle membrane, not a many-neighbor hydrophobic cohesion term.  The
sampled CGL-center range starts at
$r=5.0\,\text{\AA}$, below the DOPC-derived excluded-area contact distance
$r_{\text{contact}}=6.959\,\text{\AA}$. Inside that excluded-area domain a
Weeks--Chandler--Andersen area term is added with
$\epsilon=k_B T_{\text{production}}=0.8647\,E_{\text{up}}$ and
$\sigma=r_{\text{contact}}/2^{1/6}$.  This term represents the projected
in-plane steric area of the hidden DOPC beads.  Spline rows whose radial support
lies inside the excluded-area domain are constrained to nonnegative controls,
because attractive controls there are fitting overshoot rather than physical
excluded-volume states.  Rows below the first sampled distance are unresolved
by the spline samples, so they are assigned a finite inner barrier from the
maximum first sampled dry-MARTINI energy expectation.  This inner barrier is
therefore tied to the sampled dry-MARTINI table, not to a chosen numeric cap.
No sampled-energy clipping, SVD, empirical pair scaling, pairwise PMF, or flat
maximum-energy contact core is applied.

\paragraph{Leaflet-normal orientation term.}
The collapsed CGL particle removes the many explicit DOPC bead contacts that
otherwise keep lipid tail axes aligned with the leaflet normal.  The pair spline
above still supplies CGL--CGL excluded volume and orientation compatibility, but
the isolated pair table is not a many-neighbor membrane orientational field.
Production CGL inputs therefore add a one-body leaflet-normal term on the same
dynamic CGLD-derived orientation coordinate,
\begin{equation}
U_{\text{leaflet}} = \frac{1}{2} k_{\text{leaflet}}
    \left(n_z - n_z^0\right)^2 ,
\end{equation}
where $n_z$ is the CGL orientation-vector $z$ component and
$n_z^0 \in \{-1,+1\}$ is assigned from the initial leaflet direction.  The
spring constant is not tuned from trajectory appearance.  It is derived from
the raw CGL--CGL dry-MARTINI table by comparing, at the first-neighbor contact
radius, the table energy for in-plane CGL axes against the vertical same-leaflet
orientation.  This keeps the term tied to the same resolved-lipid physics used
to build $U_{\text{CG-CG}}$ and prevents CGLD from becoming an unconstrained
display coordinate during minimization or burn-in.

\subsection{CG Lipid -- Sidechain Quad-Spline Potential}
\label{sec:cg-sc}

The interaction between a CG lipid particle and a protein sidechain (SC)
uses the same functional form as Eq.~\ref{eq:cg-cg}, with the SC bead treated
as source~1 ($\cos\theta_1 = -\hat{\mathbf{n}}_{\text{SC}} \cdot
\hat{\mathbf{r}}_{12}$) and the CG lipid as source~2
($\cos\theta_2 = +\hat{\mathbf{n}}_{\text{CG}} \cdot
\hat{\mathbf{r}}_{12}$). The SC direction $\hat{\mathbf{n}}_{\text{SC}}$ is the
unit vector from C$_\alpha$ to C$_\beta$.

The table is built from the same dry-MARTINI energy expectation, using
$N_{\text{relax}} = 120$ bead relaxation steps and a tighter angular grid
(9 $\cos\theta$ points $\times$ 4 sidechain azimuths $\times$ 4 CGL azimuths).
For each sidechain rotamer, all resolved dry-MARTINI sidechain bead positions
are used; the fit does not collapse a multi-bead sidechain to its rotamer
center.  The sidechain bead model and the DOPC bead model are independently
rotated over the sampled SC and CGL direction vectors.  Optional bead-frame
quadrature around each sampled direction vector can be enabled when checking
convergence of the resolved-bead projection, but the spline coordinates remain
the runtime direction-vector projections.  The relaxed explicit-bead samples
also retain the bonded deformation penalty relative to the unrelaxed DOPC reference.  Separate
tables are constructed for each standard proteinogenic sidechain type present
in the active system against the single CG lipid type.

For compactness the sidechain table is stored as a low-rank angular
decomposition plus radial B-splines, but the fit no longer clips the sampled
energy or residuals to fixed values.  The short-range radial rows are assigned
the maximum first-sampled dry-MARTINI energy expectation for that sidechain
type, recorded as
\texttt{short\_range\_core\_source=max\_first\_sampled\_dry\_martini\_energy\_expectation}.
Rows whose radial support lies inside the DOPC-derived contact shell are then
constrained to nonnegative CGL-SC controls
(\texttt{excluded\_area\_source=dopc\_contact\_nonnegative\_controls}).  The
radial angular-mode amplitudes are set to zero over the same rows so that the
unresolved overlap region cannot regain an orientation-specific attraction.
This treats sub-contact CGL-SC states as excluded overlap with the hidden DOPC
molecule, while retaining the dry-MARTINI-derived attraction outside the
contact shell.  The fitted radial support is limited to $r_{\text{contact}}$;
the runtime cutoff is the fitted support plus one radial knot interval, so the
current DOPC sidechain support is approximately
$6.959 + 1.4 = 8.359\,\text{\AA}$.

\paragraph{Runtime Rotamer Coupling.}
In production inputs the CGL--SC table is evaluated as a rotamer one-body term,
\texttt{cg\_lipid\_rotamer\_sc}, rather than as an independent CB-only potential.
For each sidechain placement row and each CGL particle, the node evaluates the
same dry-MARTINI-derived CGL--SC spline above and writes one scalar energy row
with the same row ordering as \texttt{placement\_fixed\_point\_vector\_only}.
That scalar is passed to the sidechain rotamer solver together with the ordinary
SC--environment one-body table, so CGL--SC energetics affect rotamer
probabilities and protein conformational forces through the same path used by
the full-resolution explicit-lipid workflow.  This changes only the ownership of
the runtime term: the CGL--SC interaction remains active and uses the same spline
coefficients, cutoff, and coordinate derivatives.  The older standalone
\texttt{cg\_lipid\_sc} node is not generated for new inputs, preventing
double-counting outside the rotamer probability model.

\subsection{CG Lipid -- Target Directional Potential}
\label{sec:cg-iso}

Interactions between CG lipid particles and non-sidechain dry-MARTINI target
particles (water, ions, protein backbone proxy sites, and other point
environment sites) use a directional cubic B-spline over distance and lipid
orientation:

\begin{equation}
U_{\text{CG-target}}(r, \cos\theta)
= \sum_{i=0}^{N_r-1}\sum_{j=0}^{N_\theta-1}
  c_{ij}^{(X)}\,B_i(r)\,B_j(\cos\theta),
\label{eq:cg-iso}
\end{equation}

where $\cos\theta = \hat{\mathbf{n}}_{\text{CGL}}\cdot\hat{\mathbf{r}}_{12}$
and $X$ is the target MARTINI type.  The table uses $N_r=14$ radial and
$N_\theta=15$ angular control points.  It is fitted directly to explicit
DOPC--target dry-MARTINI bead energies, not to a capped effective
Lennard-Jones surrogate or a radial orientation-averaged Lennard-Jones
replacement.  For each radial sample $r$ and angular sample $\cos\theta$, the CGL center is placed at
distance $r$ from a point probe of target type $X$, the 14-bead DOPC reference
is oriented so its CGL vector has the requested dot product with
$\hat{\mathbf{r}}_{12}$, internal bead relaxation is charged by the same
relative bonded deformation penalty, and azimuthal rotations are integrated as
an energy expectation:
\begin{equation}
  U_{\text{CG-}X}(r,\cos\theta)
  =
  \left\langle
    \sum_{i\in\text{DOPC}}
    \left[
      4\varepsilon_{iX}\left(
        \left(\frac{\sigma_{iX}}{r_{iX}}\right)^{12}
        -
        \left(\frac{\sigma_{iX}}{r_{iX}}\right)^6
      \right)
      +
      k_C \frac{q_i q_X}{\epsilon_r r_{iX}}
    \right]
  \right\rangle_{\phi}.
\end{equation}
The DOPC bead charges used in this projection are the molecule charges from
\texttt{dry\_martini\_v2.1\_lipids.itp}: NC3 has charge $+1$, PO4 has charge
$-1$, and the remaining DOPC beads are neutral.  They are not inferred from
bead type alone, because the Q0 type is context-dependent and treating NC3 as
neutral would make the projected DOPC particle net negative.
The expectation includes the azimuth of the CGL direction vector around
$\hat{\mathbf{r}}_{12}$.  Thus the CGL--target table is a projection of the
resolved lipid direction-vector sampling onto the runtime variables
$(r,\cos\theta)$, not a table built from one default lipid orientation.
The resulting two-dimensional energy-expectation samples are converted to
$E_{\text{up}}$ and fitted directly with the tensor-product spline.  The
unsampled radial core below the first explicit target samples is filled from
the first resolved energy-expectation boundary row, representing a
force-field-derived unresolved core rather than a numeric energy cap.  Spline
controls whose radial support contributes inside the DOPC contact excluded-area
domain are constrained to nonnegative values.  This is the same dry-MARTINI
excluded-volume projection used for CGL--CGL: attractive controls in this
domain are spline overshoot of repulsive bead-overlap samples, not physical
target affinity.  The old
global CGL-vs-target $\sigma$ cap and radial orientation-averaged table are no
longer part of the production path; generated tables carry the source
attribute \texttt{explicit\_dopc\_directional} and energy-expectation metadata.
Legacy \texttt{martini.h5} files that still contain capped CGL effective-LJ
metadata are rejected and must be rebuilt.
Backbone carrier atoms (N, C$_\alpha$, C, O) are not independent CGL-target
particles.  The lipid/backbone target is the virtual MARTINI BB proxy site, and
forces on that proxy are projected onto the underlying Upside backbone
coordinates.  Carrier atoms still accumulate forces from sidechain/rotamer
coupling and from the projected backbone/environment path; if a direct carrier
force is present in another node, it is added to that carrier atom rather than
being re-projected as a BB-proxy force.
The dry-MARTINI backbone model follows the martinize fallback convention
with secondary structure fixed to coil (``C''): each residue is assigned a
MARTINI bead type from the coil column of the standard martinize
backbone-type table.
Residue-specific coil types are \texttt{P5} (default, most residues),
\texttt{P4} (ALA), and \texttt{Na} (PRO, HYP).
The charged-termini convention is applied in residue order:
the N-terminal residue is typed \texttt{Qd} ($+1$), the C-terminal residue
is typed \texttt{Qa} ($-1$), and each chain-break or sequence-break fragment
endpoint receives the corresponding \texttt{Qd}/\texttt{Qa} assignment.
In full-resolution lipid mode the explicit DOPC beads carry their native
MARTINI charges (NC3 $+1$, PO4 $-1$), so the terminal backbone charges
interact with the lipid environment through standard Coulomb and
MARTINI-LJ pair potentials rather than through directional CGL spline
tables.
The charged BB bead types (\texttt{Qd}, \texttt{Qa}) are part of the
standard dry-MARTINI v2.1 force field and have complete nonbonded
cross-interactions with all other particle types.  In single-particle CGL
mode, however, the directional explicit-DOPC PMF for charged terminal BB
targets is not used as an attractive additive CGL--terminal potential.  The
explicit table contains headgroup, solvent, and ion response that is no
longer represented explicitly after the lipid has been collapsed into a CGL
particle.  Reusing that charged-target well as an additive CGL projection can
over-stabilize terminal adsorption and bend exposed helices.  The runtime
therefore splits \texttt{Qd}/\texttt{Qa} BB proxy targets into
\texttt{cg\_lipid\_target\_charged\_bb\_excluded\_volume}, whose controls are
derived from the current \texttt{cg\_lipid\_target} table by retaining only
nonnegative values.  This keeps the CGL excluded-volume boundary for charged
termini while leaving their dry-MARTINI charge in the generic nonbonded model
and their BB-env hybrid coupling intact.
Mobile ions are handled by the same transferability rule.  The directional
DOPC--ion energy-expectation table is not used as an attractive additive
many-ion potential, because the single-particle lipid model has integrated out
the explicit DOPC headgroup beads and does not include the corresponding
hydration/solvent ion PMF.  The runtime splits ion targets into a separate
CGL--ion node whose controls also retain only nonnegative values.  Ordinary
uncharged BB/protein targets continue to use the full CGL-target projection.
The MARTINI log reports all \texttt{cg\_lipid\_target*} nodes in the
\texttt{cg\_lipid\_target} bucket, so \texttt{protein\_potential} contains
only Upside protein terms plus explicit SC-env and BB-env interface terms.
The validation invariant is that ions and charged termini remain ordinary
dry-MARTINI particles in generic interactions, while direct CGL interactions
with these charged targets are owned by excluded-volume target nodes.
A copied 1AFO stage-7 burn-in diagnostic from the same minimized handoff state
kept the second helix near a $40^\circ$ half-chain angle after 40k steps with
charged \texttt{Qd}/\texttt{Qa} CGL controls made nonnegative, whereas the
original attractive charged-target projection started production near
$90^\circ$.

\subsection{Hybrid Interface: Sidechain -- Environment Interaction}
\label{sec:sc-env}

Protein sidechain beads interact with the dry MARTINI environment (water and
ion beads in full-resolution lipid mode, and water, ion, and CGL environment
terms in single-particle lipid mode) through orientation-dependent one-body
potentials:

\begin{equation}
U_{\text{SC-env}}(r, \cos\theta) = V_{\text{rad}}(r)
                                 + A(\cos\theta) \cdot V_{\text{ang}}(r)
\label{eq:sc-env}
\end{equation}

where $r = |\mathbf{r}_{\text{env}} - \mathbf{r}_{\text{CB}}|$ is the distance
from the environment bead to the C$_\beta$ anchor point, and
$\cos\theta = -(\mathbf{r}_{\text{CB}} - \mathbf{r}_{\text{env}}) \cdot
\hat{\mathbf{n}}_{\text{SC}} / r$.

\paragraph{Underlying Physics.}
The tables are precomputed from the dry MARTINI nonbonded potential between a
resolved sidechain rotamer and an environment probe particle:

\begin{align}
E_{\text{LJ}}(r) &= 4\varepsilon_{ij} \left[
                    \left(\frac{\sigma_{ij}}{r}\right)^{12}
                  - \left(\frac{\sigma_{ij}}{r}\right)^{6} \right] \label{eq:lj} \\
E_{\text{Coul}}(r) &= \frac{k_C}{\epsilon_r} \frac{q_i q_j}{r} \label{eq:coul}
\end{align}

with $k_C = 138.935\,\text{kJ}\cdot\text{nm}\cdot\text{mol}^{-1}\cdot e^{-2}$
and dielectric constant $\epsilon_r = 15$. At each sampled $(r, \cos\theta)$,
the sidechain bead positions from all rotamers are placed; the total energy is
computed as the sum over SC beads of $E_{\text{LJ}}(r_{ij}) +
E_{\text{Coul}}(r_{ij})$, where $r_{ij}$ is the distance from each SC bead at
its rotamer position to the probe point.  For each rotamer, the resolved
sidechain bead model is placed over the sampled SC direction vector used by
the runtime table.  Optional bead-frame quadrature around that direction can
be enabled for projection-convergence checks. The 2D energy grid
$E(r_i, \cos\theta_j)$ is stored as a lower-bound radial table plus a
nonnegative angular penalty:

\begin{itemize}
  \item $V_{\text{rad}}(r) = \min_{\cos\theta} E(r, \cos\theta)$
  \item Residual $\Delta(r, \cos\theta) =
    \max(E(r, \cos\theta) - V_{\text{rad}}(r), 0)$ is fit with one
    nonnegative rank-1 mode, $A(\cos\theta) V_{\text{ang}}(r)$, with
    $A \ge 0$ and $V_{\text{ang}} \ge 0$.
\end{itemize}

This reconstruction can overestimate some orientations but cannot create an
orientation-specific attraction below the sampled dry-MARTINI minimum at the
same radius.  That lower-bound property is required for explicit DOPC beads,
because a negative SVD residual inside a repulsive core can otherwise become an
unphysical lipid--sidechain well during minimization and burn-in.

The resulting tables are stored as piecewise-linear grids with 96 radial points
($r \in [2.5, 12.0]\,\text{\AA}$) and 13 angular bins
($\cos\theta \in [-1, 1]$). Rotamer-resolved variants are also available
through a 1-body table used by the sidechain rotamer optimization node.  In
single-particle lipid mode, the CGL--SC spline from Sec.~\ref{sec:cg-sc} is
injected as an additional rotamer one-body term for the collapsed lipid
particle.  The ordinary SC--particle table remains active in both lipid modes
for non-CGL environment particles such as water and ions.  Full-resolution
lipid mode also uses the SC--particle table for explicit DOPC beads; CGLipid
mode replaces only those explicit-lipid SC--particle contacts with the SC--CGL
spline.  This preserves sidechain-environment ownership while letting lipid
contacts bias the sidechain rotamer ensemble.

\paragraph{Interface Scaling.}
The SC-env potential is multiplied by a global interface scale factor
$\alpha_{\text{interface}}$ (default 1.0, calibrated against implicit-membrane
reference simulations). During the hybrid simulation startup phase, SC-env
forces are linearly ramped from zero over $N_{\text{relax}} = 150$ steps with a
force cap of $25.0\,E_{\text{up}}/\text{\AA}$, while backbone degrees of freedom
are held nearly fixed by a backbone feedback mixing protocol over
$N_{\text{hold}} = 200$ steps.

\subsection{Hybrid Interface: Backbone -- Environment Interaction}
\label{sec:bb-env}

Protein backbone fragments interact with the dry MARTINI environment through
the virtual MARTINI BB proxy site.  The proxy represents the residue-level
MARTINI BB bead, while the N, C$_\alpha$, C, and O carriers are the Upside
backbone coordinates that receive projected BB-proxy forces and forces from
sidechain/rotamer coupling.  BB--environment contacts use the \textbf{standard
Martini potential}, which evaluates the combined LJ and Coulomb energy via a
precomputed cubic B-spline:

\begin{equation}
U_{\text{BB-env}}(r) = B_{\text{spline}}\bigl(r; \; 4\varepsilon(\sigma^{12}r^{-12}
                      - \sigma^6 r^{-6}) + k_C q_i q_j / (\epsilon_r r) \bigr)
\label{eq:bb-env}
\end{equation}

The combined energy $E_{\text{LJ}}(r) + E_{\text{Coul}}(r)$ is pre-tabulated on
a uniform grid of 1000 points per unique $(\varepsilon, \sigma, q_i q_j)$
triple and fitted with a layered clamped B-spline~\cite{Upside}. Forces on the
virtual backbone proxy atoms are projected onto the underlying Upside backbone
degrees of freedom.  Carrier atoms are never treated as virtual BB proxies for
projection: direct carrier sensitivities are accumulated directly on the
carrier coordinates, so sidechain/rotamer forces and projected backbone forces
are additive. Cross-interface BB--env pairs are scaled by
$\alpha_{\text{interface}}$.

\subsection{Martini Pair Ownership Protocol}

To prevent double-counting and to keep the hidden CGLD site as an internal
orientation coordinate, the generic Martini pair-list construction excludes
all pairs that contain CGL or CGLD.  Every physical interaction involving the
single-particle lipid is owned by a dedicated spline node:

\begin{itemize}
  \item CGL--CGL: handled entirely by $U_{\text{CG-CG}}$ (Sec.~\ref{sec:cg-cg}).
  \item CGL--SC: handled by the dry-MARTINI-derived $U_{\text{CG-SC}}$
    spline (Sec.~\ref{sec:cg-sc}) through the rotamer one-body node
    \texttt{cg\_lipid\_rotamer\_sc}; it is not added again as a generic or
    standalone CB potential.
  \item CGL--target: handled entirely by $U_{\text{CG-target}}$
    (Sec.~\ref{sec:cg-iso}) against water, ions, virtual BB proxy sites, and
    other non-sidechain point targets.
  \item CGLD: carries the orientation coordinate and its harmonic CGL-CGLD bond
    only; it is not a generic nonbonded particle.
  \item CGL leaflet orientation: handled by \texttt{cg\_lipid\_leaflet\_orientation},
    with its spring constant derived from the raw CGL--CGL dry-MARTINI table.
\end{itemize}

This means CGL-CGL torque, rotamer-weighted CGL-SC torque, CGL-target torque,
and leaflet-normal torque act directly on the CGLD-position-derived vector
through the same coordinate derivatives used for position forces.

With this ownership, full-resolution and single-particle lipid modes expose the
same physical protein interfaces at different lipid resolution.  Full mode
uses explicit DOPC beads in the generic MARTINI pair potential and the
SC-particle one-body table.  Single-particle mode keeps the same SC-particle
table for non-CGL environment particles, replaces explicit DOPC--DOPC with the
CGL--CGL spline, and replaces explicit DOPC--SC-particle contacts with the
CGL--SC rotamer one-body spline.  Both modes keep BB--environment contacts on
the same charged or neutral virtual BB proxy sites and route those forces to the
same carrier coordinates.  Terminal fragment endpoints remain opposite
charged in both modes: each fragment starts with \texttt{Qd} backbone sites
carrying $+1$ charge and ends with \texttt{Qa} backbone sites carrying $-1$
charge.

\subsection{Stage-6 Relaxation Protocol}

Hybrid CG-lipid systems are minimized before the rigid-protein stage-6 NPT
dynamics.  The minimization uses the same active Hamiltonian as the subsequent
stage: SC--environment, BB--environment, CGL--SC, CGL--target, CGL--CGL,
generic Martini non-CGL pairs, ions, and bonded terms remain present.  Its role
is to remove residual packing stress from the generated bilayer/protein
configuration before finite-timestep MD and production handoff.  It is not a
restraint, force scaling, interaction exclusion, or model parameter.

\subsection{Stage-7 Production Handoff and MARTINI Integration}

The standard Upside integrator implementation follows the three-stage HOH
coefficient convention of Predescu et al.~\cite{Predescu2012}.  In that
convention the per-stage momentum and position coefficients each sum to the
number of stages $q$; for the three-stage method,
\begin{align}
  \sum_i a_i &= 3, &
  \sum_i b_i &= 3 .
\end{align}
Consequently the parameter called $\Delta t$ in the HOH formula is the average
time per force evaluation, and one outer application advances a transit time
$q\Delta t$.  The shared Upside command-line scheduling already accounts for
this convention by using an internal public-time factor of three for the
standard Verlet path.  Existing Upside workflows and timestep choices are
calibrated to that engine semantics, so the hybrid workflow keeps the same
public-time convention.

The hybrid dry-MARTINI workflow keeps the same shared Upside integrator rather
than introducing a separate MARTINI integrator.  The production input timestep
remains $0.002$ in Upside command-line units; reducing it to $0.0006666667$
would make the public Upside timescale three times slower than the original
workflow convention.  The issue in the hybrid workflow is therefore not that
the Predescu coefficients are incorrect or that the protein timescale should be
rescaled; it is that the
single-particle MARTINI model combines physical MARTINI masses, a stiff
CGL--CGLD orientation carrier, tabulated CGL interface forces, and a
rigid-to-flexible protein handoff that were not part of the original
Upside-trained protein-only dynamics.

The command-line usage follows the same defaults as the ordinary Upside
examples.  The workflow does not pass \texttt{--integrator v}, because Verlet
is the default integrator, and it does not pass \texttt{--inner-step}, which is
only needed for the multi-step integrator.  The MD stages do pass
\texttt{--time-step} deliberately: equilibration uses $0.010$ and production
uses $0.002$ to set the MARTINI integration timestep while preserving the
standard public-time factor of three.  Minimization stages do not pass
\texttt{--time-step}; the minimizer is controlled by its own
\texttt{--min-step} parameter.

The dry-MARTINI masses are retained in the runtime HDF5.  Removing masses makes
the CGL and CGLD degrees of freedom artificially light and destabilizes the
stiff orientation coordinate.  Scaling pair energies by particle mass is also
not a valid substitute for a mass matrix: a pair potential is a scalar shared
by two particles with generally different masses, and mass-weighting the
energy would change the configurational Boltzmann distribution rather than only
the inertial response.

Stage 7 also changes the mechanical state of the system: stage 6 keeps the
protein rigid while relaxing the lipid/protein environment, whereas production
releases the protein under the full hybrid Hamiltonian.  Without a production
handoff relaxation, the first production segment spends a substantial part of
its trajectory lowering internal protein energy instead of fluctuating around a
prepared production basin.  Therefore the workflow performs an opt-in
stage-preserving minimization of stage 7 before MD using
\texttt{--minimize-preserve-stage}.  This minimization keeps SC--environment,
BB--environment, CGL--SC, CGL--target, CGL--CGL, generic Martini, ion, and
bonded terms active under the same production Hamiltonian that the subsequent
MD uses.
The minimization is followed by an explicit stage-7 burn-in under that same
production Hamiltonian before the named production segment is written.  This
burn-in is not a parameter change: it is ordinary NVT dynamics with the
production timestep, physical masses, active hybrid interactions, recorded
momenta, and the normal hybrid transition counter.  Its final positions and
momenta are promoted to \texttt{/input}, the burn-in \texttt{/output} is
cleared, and the public production chunk then starts from the equilibrated
interface.  Current 1AFO and 1RKL checks show that this is the window in which
CGL--SC and CGL--target contacts relax into their production basin; copied
continuations after this window fluctuate around the same total-potential
range instead of repeating the large early drop.

\subsection{Energy Units}

All potential coefficients are stored in upside energy units $E_{\text{up}}$,
where $1\,E_{\text{up}} = 2.914952774272\,\text{kJ/mol}$. Lengths are in
\r{A}ngstr\"{o}ms ($1\,\text{nm} = 10\,\text{\AA}$). The conversion is applied
at table-building time (Python) and at load time (C++), with tail corrections
subtracted so that all potentials decay smoothly to zero at their respective
cutoffs.

\subsection{Parallel Table Generation}

The dry-MARTINI parameter generator parallelizes independent table slices while
keeping all HDF5 writes in the parent process.  SC--particle tables are split by
residue and target type, CGL--SC tables by residue type, CGL--target tables by
target type, and the CGL--CGL tensor by radial/angular grid point.  The worker
count is controlled by \texttt{UPSIDE\_MARTINI\_TABLE\_WORKERS}; if it is not
set, Slurm allocations \texttt{SLURM\_CPUS\_PER\_TASK} or
\texttt{SLURM\_CPUS\_ON\_NODE} are used, otherwise the local CPU count is used
with a conservative cap for interactive M1 macOS builds.  The one-shot
generator also accepts \texttt{--workers}, \texttt{--bead-frame-count},
\texttt{--sc-bead-frame-count}, and \texttt{--cgl-bead-frame-count}.  The bead-frame
controls are optional quadrature around sampled direction vectors; they do not
change the runtime spline variables, disable interactions, or scale any
physical term.  Process workers are used first; if an environment disallows
process-pool semaphores, the generator falls back to a thread pool with the
same worker count rather than serializing the build.

% ==============================================================================
\begin{thebibliography}{9}

\bibitem{MARTINI}
Marrink, S.~J., Risselada, H.~J., Yefimov, S., Tieleman, D.~P., \& de Vries, A.~H.
``The MARTINI Force Field: Coarse Grained Model for Biomolecular Simulations.''
\textit{J. Phys. Chem. B}, 111(27), 7812--7824 (2007).

\bibitem{deBoor}
de Boor, C.
``A Practical Guide to Splines.''
Springer (1978).

\bibitem{Upside}
Jumper, J.~M., Faruk, N.~F., Freed, K.~F., \& Sosnick, T.~R.
``Accurate calculation of side chain packing and free energy with
applications to protein molecular dynamics.''
\textit{PLoS Comput. Biol.}, 14(12), e1006342 (2018).

\bibitem{Predescu2012}
Predescu, C., Lippert, R.~A., Eastwood, M.~P., Ierardi, D.~J., Xu, H.,
Jensen, M.~O., Bowers, K.~J., Gullingsrud, J., Rendleman, C.~A.,
Dror, R.~O., \& Shaw, D.~E.
``Computationally efficient molecular dynamics integrators with improved
sampling accuracy.''
\textit{Molecular Physics}, 110(9--10), 967--983 (2012).

\end{thebibliography}

\end{document}
